---
title: "WUP_04"
author: "April Galvan"
date: "Fall 2021"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(knitr)
require(tidyverse)
require(tigerstats)

```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

The data is in the file GSScsv.csv and came from the 2018 General Social Survey.  The question to answer is to resolve this hypothesis.  
$H_0$ There is no difference between the average score on the WORDSUM test and level of schooling DEGREE  
$H_a$ There is a significant difference in average score on the WORDSUM test between at least two levels of DEGREE  

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
mydata<-read.csv(file="GSScsv.csv")
```
```{r}
boxplot(WORDSUM~DEGREE,data=mydata)
```

When looking at the boxplot, we can see that the middle box can go completely under the box labeled "Graduate" and "Junior College." This means that there is no interaction between the boxes and the means of the sets are completely different. Therefore,if you run any test with the boxes, you can suspect middle box's mean value for WORDSUM is lower than any of the other boxes labeled "Bachelor," Graduate," and "Junior College."

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
favstats(WORDSUM~DEGREE,data=mydata)
```

The individuals with Junior College degrees, Bachelor’s degrees, and Graduate degrees have a higher mean than those in high school and junior high school category. People with higher degrees have a mean of 9 or higher and those in the high school and junior high school category have a mean of 8 or less. 

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->
```{r}
model1 <- aov(WORDSUM~DEGREE,data=mydata)
summary.aov(model1)
```

The P value seems very small. The P value represents the chances of getting the same results when the null hypothesis is actually true. I don't believe that, therefore I reject the null hypothesis.

```{r}
#we specify the margins starting at the bottom and proceeding clockwise - thus 8.7 is the left side margin to hold the names of the factors
par(mar = c(3, 15, 2, 2))
plot(TukeyHSD(model1,conf.level=.95),las=2)
```

From what we can see, high school-graduate are different from each other. Also, LT high school-graduate are different from each other. The dotted line in the middle does not cross into the high school-graduate or LT high school-graduate confidence level.

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
